% Sample file on how to use subfiles.
\documentclass[preface.tex]{subfiles}

\begin{document}

This thesis concludes my Master of Science education in Engineering Mathematics at Chalmers University of Technology. The thesis was worked on throughout the spring of 2013 which was my tenth semester at Chalmers.

I would first want to greatly thank my supervisor Associate Professor Magnus Ekh at the Division of Material and Computational Mechanics, Chalmers. He has been the person that I have approached with any issues I have had regarding the writing of the thesis.  He have also given a lot of feedback regarding the language and grammar used. I would also like to thank Professor Göran Wahnström at the Division of Materials and Surface theory, Chalmers, for contacting me about the opportunity to do this thesis. 

Thanks also go out to my friends and family who have supported me during not only the writing of this thesis, but during all of my five years studying at Chalmers. Special thanks goes to Martin Gren, Olof Ahlén, Petter Säterskog and Patric Holmvall who have been my main collaborators regarding school work during these five year. I would also like to give thanks to my brother Rikard Carlsson for the countless hours of Skype conversations that have been a constant source of laughter.

Before this thesis I had not had very much experience with Computational Mechanics. These six months have therefore exposed me to many new methods and tools that will certainly be of use later in my academic career. I have now been given the opportunity to continue my research performed in this thesis by working at the department this summer. I very much look forward to this and it feels like a great way to start off after completing the thesis.

\textit{Kristoffer Carlsson, Gothenburg, 2013.}
\end{document}
